### 2022-03-24 draft.tex
Deploying to gh-pages from @ emuise/ms-assessingRepresentation@78811d9bfc10ec64ca2c6fa6fc5d520683129737 🚀

\hypertarget{tbl:bec-table}{}
\begin{longtable}[]{@{}lllll@{}}
\caption{\label{tbl:bec-table}Number of subzones, total area, and
percent protected by BEC Zone.}\tabularnewline
\toprule
Zone & Zone Name & \# of Subzones & Area (ha) & \%
Protected\tabularnewline
\midrule
\endfirsthead
\toprule
Zone & Zone Name & \# of Subzones & Area (ha) & \%
Protected\tabularnewline
\midrule
\endhead
BAFA & Boreal Altai Fescue Alpine & 2 & 6,286,778 &
30.1\%\tabularnewline
BG & Bunchgrass & 2 & 257,072 & 11.8\%\tabularnewline
BWBS & Boreal White and Black Spruce & 5 & 16,404,142 &
8.6\%\tabularnewline
CDF & Coastal Douglas-fir & 1 & 251,232 & 4.8\%\tabularnewline
CMA & Coastal Mountain-heather Alpine & 3 & 3,574,039 &
17.9\%\tabularnewline
CWH & Coastal Western Hemlock & 10 & 10,795,067 & 19.5\%\tabularnewline
ESSF & Engelmann Spruce -- Subalpine Fir & 43 & 17,465,113 &
17.8\%\tabularnewline
ICH & Interior Cedar -- Hemlock & 12 & 5,538,842 & 10.2\%\tabularnewline
IDF & Interior Douglas-fir & 12 & 4,488,085 & 5.9\%\tabularnewline
IMA & Interior Mountain-heather Alpine & 2 & 1,257,949 &
29.2\%\tabularnewline
MH & Mountain Hemlock & 6 & 4,059,301 & 19.8\%\tabularnewline
MS & Montane Spruce & 8 & 2,863,394 & 9.4\%\tabularnewline
PP & Ponderosa Pine & 1 & 294,985 & 7.1\%\tabularnewline
SBPS & Sub-Boreal Pine -- Spruce & 4 & 2,265,365 & 9.5\%\tabularnewline
SBS & Sub-Boreal Spruce & 11 & 10,337,497 & 6.7\%\tabularnewline
SWB & Spruce -- Willow -- Birch & 6 & 8,655,855 & 23.3\%\tabularnewline
\bottomrule
\end{longtable}

@@

\hypertarget{tbl:vector-table}{}

@@

\caption{\label{tbl:vector-table}Mean values of forest structural
attributes in protected areas (PA), unprotected areas (UA), as well as
the percent difference between the means. Zones with more than a 5\%
difference are bolded.}\tabularnewline

>>>>

\begin{longtable}[]{@{}lllll@{}}
\caption{Number of subzones, total area, and percent protected by BEC
Zone.\{\#tbl:bec-table\}}\tabularnewline
\toprule
Zone & Zone Name & \# of Subzones & Area (ha) & \%
Protected\tabularnewline
\midrule
\endfirsthead
\toprule
Zone & Zone Name & \# of Subzones & Area (ha) & \%
Protected\tabularnewline
\midrule
\endhead
BAFA & Boreal Altai Fescue Alpine & 2 & 6,286,778 &
30.1\%\tabularnewline
BG & Bunchgrass & 2 & 257,072 & 11.8\%\tabularnewline
BWBS & Boreal White and Black Spruce & 5 & 16,404,142 &
8.6\%\tabularnewline
CDF & Coastal Douglas-fir & 1 & 251,232 & 4.8\%\tabularnewline
CMA & Coastal Mountain-heather Alpine & 3 & 3,574,039 &
17.9\%\tabularnewline
CWH & Coastal Western Hemlock & 10 & 10,795,067 & 19.5\%\tabularnewline
ESSF & Engelmann Spruce -- Subalpine Fir & 43 & 17,465,113 &
17.8\%\tabularnewline
ICH & Interior Cedar -- Hemlock & 12 & 5,538,842 & 10.2\%\tabularnewline
IDF & Interior Douglas-fir & 12 & 4,488,085 & 5.9\%\tabularnewline
IMA & Interior Mountain-heather Alpine & 2 & 1,257,949 &
29.2\%\tabularnewline
MH & Mountain Hemlock & 6 & 4,059,301 & 19.8\%\tabularnewline
MS & Montane Spruce & 8 & 2,863,394 & 9.4\%\tabularnewline
PP & Ponderosa Pine & 1 & 294,985 & 7.1\%\tabularnewline
SBPS & Sub-Boreal Pine -- Spruce & 4 & 2,265,365 & 9.5\%\tabularnewline
SBS & Sub-Boreal Spruce & 11 & 10,337,497 & 6.7\%\tabularnewline
SWB & Spruce -- Willow -- Birch & 6 & 8,655,855 & 23.3\%\tabularnewline
\bottomrule
\end{longtable}

@@

@@

\caption{Mean values of forest structural attributes in protected areas
(PA), unprotected areas (UA), as well as the percent difference between
the means. Zones with more than a 5\% difference are
bolded.\{\#tbl:vector-table\}}\tabularnewline
